Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-03-20 documents/cpm.tex
Changes to Hogg's comments

\title{
  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
 \\ 
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
  }
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
%%   NASA Ames Research Center}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
%%   Courant Institute of Mathematical Sciences, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
%%   Department of Physics, Oxford University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
%%   Harvard--Smithsonian Center for Astrophysics}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
%%   Department of Physics and Astronomy, University College London}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
%%   McWilliams Center for Cosmology, Carnegie Mellon University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
%%   Department of Astronomy, California Institute of Technology}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
%%   Department of Astronomy, Columbia University}

@@

Let's consider a particular pixel $m$ in the focal plane in one particular month
(here we always use data per month rather than quarter,  
since there is discontinuity between every 30-ish-day period).\Bernhard{as an aside: I wonder whether \name reduces these discontinuities at all? (if we were to apply it across the discontinuities)}
\Dun{I don't think \name\ will be applied across the discontinuities, especially when auto-regression are applied,  but in the end,  the \name somehow reduces the discontinuities, since it put light curve of every month into the same base line.}

In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files on MAST
  \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
  see the \project{Kepler Archive Manual} 
  \footnote{\url{http://archive.stsci.edu/kepler/manuals/archive_manual.pdf}}).
We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m',n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Assuming that they are affected by similar systematic errors as the target star pixels, we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
   To rule out any direct optical cross-talk by starry 
light, we require that the predictor pixels are from stars
sufficiently far away from the target star (at least 20 pixels distance on the CCD).
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

When we are predicting the measurement $I_{m,n}$ from pixel $m$ at a particular time $t_n$,
  we are going to use a train-and-test framework in which not only do we not use
  data at time $t_n$ in optimizing the parameters of the regression or fit,
  but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
  where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
That is, we train (optimize fit parameters) using the \emph{time set} $\set{N}_n$ of time
  indices $n'$ such that for all $n'\in\set{N}_n$,
  $t_{n'}$ is in the same quarter as $t_n$,
  and $|t_{n'} - t_n|>\Delta t$.
The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
  nor any of its neighbors in a time window of half-width $\Delta_t$.

@@

In addition to pixel set $m'\in\set{M}_m$ from other stars,  
  we also include past and future of the target star --- autoregressive (AR) component as input 
  to remove more of the stellar variability and thus increase the sensitivity for transits. 
To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
  around the point of time $t_{n}$ being corrected, 
  to ensure that we do not remove the transit itself and then use $S$ closest future and past time points. 
That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
  in which every component $v$ is defined to be     
\begin{eqnarray}
I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
\quad,
\end{eqnarray}
\Bernhard{I find the notation $I_{mn-R-k}$ confusing --- better write $I_{m,n-R-k}$, and then for consistency also $I_{v,n}$ etc.}
where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} \Dun{I changed k to be $1,2\dots, S$ so, so for every pixel, $2S$ are used} 
  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$

>>>>

\title{
  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
 \\ 
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
  }
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}

@@

Let's consider a particular pixel $m$ in the focal plane in one particular month
  (here we always use data per month rather than quarter,  since there are discontinuities between every 30-ish-day period).
In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{m,n}$
  of the intensity falling in pixel $m$ at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{m,n}$ here we are using pixels from the Target Pixel Files on MAST
  \footnote{\url{http://archive.stsci.edu/kepler/}}, for details of the TPF, 
  see the \project{Kepler Archive Manual} 
  \footnote{\url{http://archive.stsci.edu/kepler/manuals/archive_manual.pdf}}).
We want to build a prediction for the intensity $I_{m,n}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m',n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Assuming that they are affected by similar systematic errors as the target star pixels, we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
   To rule out any direct optical cross-talk by starry 
light, we require that the predictor pixels are from stars
sufficiently far away from the target star (at least 20 pixels distance on the CCD).
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

When the measurement $I_{m,n}$ is being predicted from pixel $m$ at a particular time $t_n$,
  train-and-test framework is used, in which not only
  data at time $t_n$ are not used in optimizing the parameters of the regression or fit,
  but we don't even use any times $t$ such that $|t-t_n| < \Delta t$,
  where $\Delta t\sim 10$\,h as shown in Fig.~\ref{train-and-test}.
That is, the model is trained (optimize fit parameters) by using the \emph{time set} $\set{N}_n$ of time
  indices $n'$ such that for all $n'\in\set{N}_n$,
  $t_{n'}$ is in the same month as $t_n$,
  and $|t_{n'} - t_n|>\Delta t$.
The time set of indices $\set{N}_n$ therefore does not overlap the time point $t_n$,
  nor any of its neighbors in a time window of half-width $\Delta_t$.

@@

In addition to the pixel set $m'\in\set{M}_m$ from other stars,  
  we also include the past and future of the target star --- autoregressive (AR) component as input 
  to remove more of the stellar variability and thus increase the sensitivity for transits. 
To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
  around the point of time $t_{n}$ being corrected, 
  to ensure that we do not remove the transit itself 
  and then use $S$ closest future and past time points subject to that exclusion. 
That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
  in which every component $v$ is defined to be     
\begin{eqnarray}
I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
\quad,
\end{eqnarray}
where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} \Dun{I changed k to be $1,2\dots, S$ so, so for every pixel, $2S$ are used} 
  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$
